%% start of file `template.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,letterpaper,sans]{moderncv}   
% possible options include font size ('10pt', '11pt' and '12pt'), 
%                          paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and 
%                          font family ('sans' and 'roman')

\renewcommand{\labelitemi}{$\star$}
%%\renewcommand{\labelitemi}{$\vcenter{\hbox{$\star$}}$}

\def\Resume{{r\'{e}sum\'{e}}}

% moderncv themes
\moderncvstyle{classic} % casual (default), classic, oldstyle, banking
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc} 

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}           % if you want to change the width of the column with the dates
%\setlength{\maketitlenamewidth}{10cm}        % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
%\usepackage{helvet}
\usepackage{mathpazo}
\renewcommand{\sfdefault}{ppl}

% personal data
\firstname{Martin}
\familyname{Walsh}
\title{Linux System Administrator}
\address{~}{Evanston, IL 60202}
\email{sysadm@mwalsh.org}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Objective}

Seeking a challenging, and multifaceted, system administration position 
requiring the creative application of open source technology.

%\section{Overview}
%\begin{itemize}
%\item Passionate, hard working professional with more than 10 years experience 
%serving small businesses.
%\item Demonstrated ability to analyze business issues; efficient, accurate, 
%detail-oriented, highly skilled at resolving problems, and a track record of 
%success with high responsibility.
%\item Amiable and professional, with both a sense of humor and a strong 
%commitment toward success.
%\item Versatile and able to coordinate multiple projects, shifting to cover a 
%multitude of positions as needed.\newline
%\end{itemize}

\section{Professional Experience}

\cventry{2005--Present}{System Administrator}{Parity Systems}{Evanston}{Illinois}{Responsible for the installation, maintenance and documentation of all hardware and network services for use by internal staff and clients. Closely supported the development efforts of all web projects; configuring, deploying, and securing hosting environments/web stack.
\newline{}Notable achievements:%:
\begin{itemize}%
\item Implemented a comprehensive network monitoring and performance graphing solution (nagios, Python/Jython, Java, rrdtool).
  \begin{itemize}%
  \item Programmed more than 20 custom checks for unusual hardware and services.
  \item Created a utility framework for rapid development of new service checks.
  \end{itemize}
\item Developed a 1-wire based server room, climate sensor network and monitoring solution for less than \$100 (owfs, nagios, Python).
\item Evaluated several free and/or open source virtualization management technologies (VMware-server, ESXi, KVM/libvirt, Proxmox, etc.)
\item Assembled a Debian-based USB/LiveDVD disaster recovery environment (dnsmasq, pxe, clonezilla, dokuwiki, subversion, puppet).
\item Built an OpenOffice.org/LibreOffice headless Live CD-ROM image to provide scalable ODT to PDF conversion services to internally hosted Java web applications (BartPE, LibreOffice, OOoServer, KVM/Proxmox).%\newline%
%\item Provided oversight and documentation of critical business systems. Installed and maintained the company Wiki; primary contributor of system documentation.
%\item Automated AS/400 configuration, monitoring and reporting tasks to improve responsiveness of legacy support requests and to simplify administration (Jython, JTOpen).
%\item Created a website-to-PDF screen capturing web service to facilitate acceptance of content change requests (Python, Selenium, pdftk).
%\item Migrated Windows 2000 domain to open source alternative: Samba 3, OpenLDAP, cups
%\item Installed and configured an OpenBSD/pf based "bump-in-the-wire" transparent firewall.
%\item Developed general purpose and extensible FTP and LPD daemons, in Python, which were subsequently used in several internal development projects.
%\item Developed an MS Office 2010 conversion service, with a Python xmlrpclib front-end, to convert office documents into open formats.
%\item Wrote and maintained a collection of Python utility modules for common system tasks.
\end{itemize}}

\cventry{2000--2005}{IT Manager}{RS Industrial}{Buford}{Georgia}{Provided corporate leadership and manpower for all IT initiatives.
\newline{}Notable achievements:%:
\begin{itemize}%
\item Supervised the development of, both industrial and retail, e-commerce websites (Java, Apache Tomcat, Python, Zope).
  \begin{itemize}%
  \item Contributed Java code to integrate with credit card, payment gateway service.
  \item Developed a custom Zope "Product" to facilitate content updates by non-techincal staff.
  \end{itemize}
\item Cooperated in planning and oversight of the construction of a second building/location, including the design and installation of combined network.
\item Designed and developed automated reports based on sales and inventory datai (MS Excel/VBA, MS SQL Server, Python).
\item Implemented a voice call notification system (nagios, festival, Python, xmlrpclib, pyserial, Hayes command set)
\item Researched, recommended and purchased new technology for the entire organization.%\newline%
%\item Participated in both retail and industrial product launches. 
%  \begin{itemize}
%  \item Lead a small team to design product packaging and sales literature.
%  \end{itemize}
%\item Developed several customer service database features, furnishing automation and integration,and providing commonly requested functionality (FileMaker, MS Dynamics).
%\item Introduced open source software to provide network services at a greatly reduced cost (Postfix, spamassasin, amavisd, BIND, dhcpd, hylafax (print-to-fax), Samba, cups, nagios).
\end{itemize}}

\section{Key Skills}
\cvitem{Systems}{Linux (Debian, RHEL), Windows (all variants), iSeries AS/400, OpenBSD, Solaris}
\cvitem{Network}{Apache, Apache Tomcat, ActiveMQ, Postfix, Sendmail, Courier, Dovecot, OpenVPN, OpenSSH, Samba, OpenLDAP, BIND, ISC DHCP, CUPS, netfilter/iptables, pf, OSSEC}
\cvitem{Databases}{PostgreSQL, MySQL, CouchDB/Couchbase, OS/400 DB2}
\cvitem{Languages}{Python, bash (fluent), Java, Ruby, PHP (moderate), Perl, C (novice)}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Hiring Manager}{}
\date{April, 2012}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
\enclosure{\Resume}
\makelettertitle

Please forgive the form letter. If you are a hiring manager or recruiter seeking a talented
System Administrator, to fill a position in your organization, I suggest you contact me 
directly to discuss my qualifications in greater detail. 

\emph{\newline{}Experienced Linux System Administrator}

With 12 years of experience, I am at ease managing a diverse network of computer systems and associated
services. My most recent work experience is decidedly web-centered, but I believe that my unique
skillset supports an efficient transition into almost any business context. 

\emph{\newline{}Versatile, Amiable and Professional}

Throughout my career, I have worked in relatively small environments with a high degree of 
responsibility, as the sole system administrator; necessitating a great deal of flexibility, and 
effective interpersonal, communication and organizational skills. Consequently, I am comfortable working 
with all levels of staff, regardless of technical proficiency, and I quickly build a reputation 
for getting things done. 

\emph{\newline{}Open Source Technologist}

I have extensive experience utilizing Linux and other open source software to provide versatile and 
innovative solutions, and I am passionate about solving problems, particularly those well suited to 
automation. Although, I enjoy digging into \emph{all} kinds of difficult technical challenges, recognizing 
that they often require learning a new skill, concept or technique; and providing a solution, means 
helping someone in a tangible way.\newline

Thank you for taking the time to review my enclosed \Resume. Should you have any questions, please
contact me at the email address provided.

\makeletterclosing

\end{document}


%% end of file `resume.tex'.
