%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Systems Engineer} % Job title
    {Rocketmiles} % Organization
    {Chicago, IL} % Location
    {2016--2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Established infrastructure automation using Ansible and Terraform.}
        \item {Built a bootstrapping, docker-based, and fully automated CI/CD pipeline with Jenkins, ECS, ECR, Ansible, Terraform, Groovy.}
        \item {Developed chatbot scripts to trigger builds, test and/or deployments, and respond on success or failure using Hubot, Coffeescript.}
        \item {Extended Ansible with custom modules providing a less error-prone, automated blue-green deployment process on ElasticBeanstalk.}
        \item {Provisioned an ELK stack (elasticsearch, beats, kibana, grafana, cloudwatch, S3 etc.) providing centralized logging and monitoring.}
        \item {Created a general-purpose performance and load testing suite for diagnosing issues and performance comparisons during deployments.}
        \item {Designed, implemented and proctored the systems-engineering challenge to facilitate evaluation of prospective hires.}
        \item {Helped to guide the scope and vision of a newly formed systems engineering team.}
        \item {Provided systems engineering domain expertise in support of the ongoing development and deployment of several selling platforms.}
        \item {Assisted in the launch of two new whitelabel web products, by building production infrastructure and ancillary services on a tight timeline.}
        \item {Authored a business continuity plan.}
      \end{cvitems}
    }
    {
      \begin{cventrysummary} % Summary Statement
        First systems engineering hire. \\
        100\% Cloud: AWS (RDS | Aurora | ElastiCache | EC2 | ELB | Beanstalk | EBS | EFS | ECS | ECR | Lambda | S3 | EMR | Redshift), Compose, Cloudflare.
      \end{cventrysummary}
    }

%---------------------------------------------------------
  \cventry
    {Sr. DevOps Engineer} % Job title
    {Jellyvision} % Organization
    {Chicago, IL} % Location
    {Jul 2016--Sep 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identified and contributed improvements to the onboarding procedure for new DevOps engineering hires.}
        \item {Established stop-gap redundancy for a highly critical, customer facing, authentication system.}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {Sr. Systems Engineer} % Job title
    {Wellspring Worldwide} % Organization
    {Chicago, IL} % Location
    {2015--2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked closely with dev teams to improve the performance and stability of production applications.}
        \item {Implemented a performance testing suite using Python, Ruby, matplotlib/seaborn, Apache, JMeter.}
        \item {Hosted weekly training sessions for Ops staff covering topics such as configuration management, centralized logging, and monitoring.}
        \item {Implemnted automated testing and deployment (ChatOps-style) for several in-house apps using Slack, Hubot, Jenkins.}
        \item {Setup an ELK stack to provide centralized logging services for web and mail logs.}
        \item {Instituted a new workflow for config management activities based on best practices including unit/acceptance tests.}
        \item {Provided guidance related to cultural change (DevOps), systems engineering planning and priorities.}
        \item {Built an automated RPM builder with Docker and Jenkins.}
      \end{cvitems}
    }
    {
      \begin{cventrysummary}
        Geographically distributed cloud (AWS), datacenter, and on-site infrastructure: \\ MariaDB/Percona MySQL, PHP, Apache, Mesos, Cassandra, Zookeeper, RabbitMQ, VMWare.
      \end{cventrysummary}
    }


\newpage
{\vspace*{3ex} % <----
}

%---------------------------------------------------------
  \cventry
    {Sr. Systems Engineer} % Job title
    {Leapfrog Online} % Organization
    {Evanston, IL} % Location
    {2012--2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in two large-scale datacenter migrations with minimal downtime.}
        \item {Provided in-house, systems-engineering focussed training to cross-functional audiences, covering topics such as: \\
              • Nagios configuration best practices and custom plugin development \\
              • Puppet best practices, development workflow and testing \\
              • Dashboard creation and data analysis with Kibana/Grafana \\
              • SSL/HTTPS, DNS and domain registration
        }
        \item {Created or maintained more than 75 custom Puppet modules, parser functions, providers and facts.}
        \item {Developed a lightweight Puppet dashboard replacement that included endpoints for monitoring integration.}
        \item {Automated the reproducible build-out of a comprehensive disaster recovery environment.}
        \item {Implemented helper scripts to automate config management tasks including unit/acceptance testing, catalog diff and full context render.}
        \item {Shepherded a chatbot used extensively for automated deployments, nagios management and alerting, and orchestration of routing tasks.}
        \item {Managed a Nagios instance with approximately 1800 service checks.}
        \item {Wrote custom nagios plugins and notification handlers.}
        \item {Created Docker images for local testing by fellow software and systems engineers.}
        \item {Replaced Windows DNS with BIND automation allowing a self-service workflow based on standard deployment procedures.}
      \end{cvitems}
    }
    {
      \begin{cventrysummary}
        Datacenter and on-premise infrastructure. \\
        Responsible for system performance, reliability and security of all customer-facing infrastructure. \\
        Apache, Nginx, HAProxy, RabbitMQ, Redis, GitHub Enterprise, Make, Jenkins, Ansible, Puppet, PuppetDB, Hiera, Graphite, ELK, Grafana
      \end{cventrysummary}
    }

{\vspace*{3ex} % <----
}
%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Parity Systems, Ltd.} % Organization
    {Evanston, IL} % Location
    {2005--2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported developers and end-users alike, by providing documentation, training and bug reports.}
        \item {Constructed a server-room climate monitoring system for less than \$100 with owfs, Nagios and Python.}
        \item {Automated mainframe configuration, monitoring and reporting tasks using Jython, JTOpen.}
        \item {Developed several special-purpose network applications (FTP, LPD, xmlrpc) used for internal projects.}
        \item {Implemented a comprehensive network and performance monitoring solution using Nagios, Python/Jython/Java, and rrdtool.}
        \item {Created a debian based thumb-drive disaster recovery environment.}
        \item {Built an bootable, immutable operating system image to provide distributed PDF conversion services for an internally hosted Java app.}
        \item {Implemented an OpenBSD/pf-based ”bump-in-the-wire” transparent firewall.}
      \end{cvitems}
    }
    {
      \begin{cventrysummary}
        Solo linux system administrator, responsible for the care and feeding of all network services and hardware used by internal staff and clients:
        Tomcat, PostgreSQL, Samba, Nagios, VMWare, ESXi, KVM/libvirt, Proxmox, dnsmasq, PXE/netboot, Subversion, Selenium, AS/400, DB/400
      \end{cventrysummary}
    }

{\vspace*{3ex} % <----
}
%---------------------------------------------------------
  \cventry
    {IT Manager} % Job title
    {RS Industrial} % Organization
    {Buford, GA} % Location
    {2000--2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched, recommended and purchased new technology for the entire organization.}
        \item {Coordinated, planned and assisted in overseeing the construction of a second office space and shared LAN.}
        \item {Supervised the development of wholesale and retail ecommerce web sites.}
        \item {Integrated disparate accounting and customer service platforms, to reduce duplicate entry.}
        \item {Developed several custom customer service platform features, in Filemaker Pro, to automate common tasks.}
        \item {Automated weekly sales reporting to save time and increase accuracy.}
        \item {Created a voice-call alerting system with Nagios, festival text-to-speech, Python and pyserial.}
        \item {Programmed the PLC of an adhesive extruder for manufacturing products to customer specifications.}
      \end{cvitems}
    }
    {
      \begin{cventrysummary}
        Standalone sysadmin and IT help desk, providing corporate leadership and support for the entire organization: \\
        MS Exchange, Active Directory, Postfix, Spamassassin, BIND, dhcpd, Hylafax/cups, Samba, Nagios, Filemaker Pro, MS Great Plains.
      \end{cventrysummary}
    }

%---------------------------------------------------------
\end{cventries}
